Type Visualization for R

### 2020-06-18 paper/main.tex
paper: Initial limitations and future work

\section{Discussion}

\todo{Point limitations.}

@@

\section{Conclusion and Future Work}

>>>>

\section{Limitations and Future Work}

{\sc TypeVis} suffers from a number of shortcomings
and does not fully address the entire range of possible tasks
a language designer may need to perform.

In particular, R supports a wide range of data types
including types that contain dimensionality information.
For example, an R array may have type {\tt integer[3]}
indicating that it is an array of length $3$.
This will get compressed down into a single array
type labeled {\tt integer[]}.
Reducing the number of types can make the visualization
more understandable---at the expensive of losing some
precision in type information.
Ideally a user would be able to interactively tune
the level of type granularity based on their interest
in a specific property.
Such a feature would be especially helpful for R
since values can come attached with relevant additional
data such as the dynamic dispatch method
or user-specified metadata.

Filtering is an central mechanism in the system,
but it also comes at a cost.
If one has a specific function or several functions
in mind, then {\sc TypeVis} provides a useful
local view of that type information.
However, it does not support any kind of global
view of type information across a large amount of
functions. When the number of flows or nodes
becomes too great, the visualization will start
paginating, making comparisons over large amounts
of data impossible.
Aggregation and summarization would be key to
making a global view of the data feasible---that
remains future work.

@@

\section{Conclusion}
